The Three Corridors

### 2015-01-10 msr.tex
bulk add

>>>>

\begin{figure}
\centering
\includegraphics[scale=0.65]{dsl-usage}
\caption{DSL language usage in Java projects}
\label{fig:dsl-usage}
\end{figure}

\begin{table}
\centering
\caption{Popular DSL Usage Combinations}
\label{tbl:dsl-top-usage}
\begin{tabular}{l r}
 \hline
\textbf{DSLs} & \textbf{Count}\\
\hline
XML & 1,561\\
Regex & 909\\
SQL & 493\\
XML, XSLT & 475\\
Regex, XML, XSLT & 158\\
Regex, XML & 303\\
SQL, XML & 162\\
Regex, SQL & 116\\
Regex, SQL, XML, XSLT & 80\\
Regex, SQL, XML & 71\\
SQL, XML, XSLT & 54\\
XML, XPath & 50\\
XML, XPath, XSLT & 39\\
Regex, XML, XPath, XSLT & 38\\
HTML & 23\\
Regex, XML, XPath & 20\\
Regex, SQL, XML, XPath, XSLT & 18\\
SQL, XML, XPath, XSLT & 11\\
HTML, Regex, XML & 10\\
HTML, XML & 10\\
\hline
\end{tabular}
\end{table}
